Week 3 Notebook

### 2022-02-25 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

---
title: "Week 3 Notebook"
output: html_notebook

@@

@@

@@

## Network Attributes
 summary(smugEL_ig)
          # Vertices =  
          # Directed = 
          # hyper = 
          # loops = 
          # multiple = 
          # bipartite = 
          # total edges = 
                # missing edges =
                # non-missing edges = 
          # Vertex attribute names:
          # Edge Attribute Names: 
```

>>>>

---
title: "Week 3 Notebook"
output: html_notebook
---

```{r setup, Libraries, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

# Document Creation
library(knitr)
library(markdown)
library(yaml)
library(distill)
library(blogdown)

# Basic Analysis
library(ggplot2)
library(tidyverse)
library(clipr)
library(dbplyr)
library(data.table)
library(stringr)
library(stringi)
library(tibble)
library(tidyr)

# SNA - Social Network Analysis

library(tergm)
library(ergm)
library(network)
library(networkDynamic)
library(networkDynamicData)

library(statnet)
library(igraph)
library(igraphdata)
library(tsna)
library(sna)

```{r Set Working Directory, include=FALSE}
getwd()

setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments/sna_Week3")

## Basic R: Import & Clean Data

```{r Read raw data into R}

library(readr)

indx_SmugglerCove_recip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv", 
    col_names = FALSE, 
    col_types = cols(X1 = col_skip(),
                     X4 = col_skip()), 
                    na = "empty")

View(indx_SmugglerCove_recip)
summary(indx_SmugglerCove_recip)

 # Smuggler's Cove

smugCovIdx <- indx_SmugglerCove_recip

```{r Getting Information on a Dataset:, echo=FALSE}

# list the structure of smugCovIdx
str(smugCovIdx)

# class of an object (numeric, matrix, data frame, etc)
class(smugCovIdx)

# list the variables in smugCovIdx
names(smugCovIdx)

# dimensions of an object
dim(smugCovIdx)
```

```{r & Clean Data}

  library(stringr)
# DATA Cleaning

      # Drop NA rows
smugCovIdx <- na.omit(smugCovIdx)

#####
#     Drop it like...
#####
      # DROP COLUMNS FROM DATA FRAME

smugCovIdx = subset(smugCovIdx, 
                       select = -c(4)
                       )

#####

#     Extract variables
#####

          # extract first word of the column, adds values in new Column at the end of DF

                    #1st pastIt
passIt <- smugCovIdx

colnames(passIt)
                    #2nd passIt
passIt$substring_first <- str_extract(passIt$X5,"(\\w+)")

#####

#####
#     Give Variables a human name
#####

# rename column names with human language

                      # Return it
colnames(passIt)
smugCovIdx <- passIt

colnames(smugCovIdx)
names(smugCovIdx )[1] <- "dnkNam"
names(smugCovIdx )[2] <- "ingNam"
names(smugCovIdx )[3] <- "dnkIng"
names(smugCovIdx )[4] <- "ingTyp"
colnames(smugCovIdx)
```

#   Project Varriables

    Raw Data:
  indx_SmugglerCove_recip

    DataFrame:
  smugCovIdx
            "dnkNam" "ingNam" "dnkIng" "ingTyp"
  network_nodes <- smugCovIdx << "dnkNam"

    Matrix:

    Network Objects: EDGE LIST

@@

smugEL_sn

[1] "network"

Network attributes:
  vertices = 274 
  directed = TRUE 
  hyper = FALSE 
  loops = FALSE 
  multiple = TRUE 
  bipartite = FALSE 
  total edges= 672 
    missing edges= 0 
    non-missing edges= 672

 Vertex attribute names: 
    dnkNam vertex.names

 Edge attribute names: 
    dnkIng ingTyp

@@

gtrans(smugEL_sn)
proportion of transitive triads

symmetrize( smugEL_sn, rule = "weak") 
symmetrize so i<->j iff i->j OR i<-j

symmetrize( smugEL_sn, rule = "strong") 
symmetrize so i<->j iff i->j OR i<-j

dyad.census(smugEL_sn) 
MAN dyad census

triad.census(smugEL_sn) 
standard directed triad census

@@

## Network Attributes
 summary(smugEL_ig)
          # Vertices =  
          # Directed = 
          # hyper = 
          # loops = 
          # multiple = 
          # bipartite = 
          # total edges = 
                # missing edges =
                # non-missing edges = 
          # Vertex attribute names:
          # Edge Attribute Names: 
```
smugEL_ig

[1] "igraph"

Network attributes:
  vertices = 274 
  directed = FALSE
  hyper = FALSE 
  loops = FALSE 
  multiple = TRUE 
  bipartite = FALSE 
  total edges= 672 
    missing edges= 0 
    non-missing edges= 672

 Vertex attribute names: 
    dnkNam vertex.names

 Edge attribute names: 
    dnkIng ingTyp
